Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-05 sections/pitfalls.tex
updated pitfalls.tex by including figure

\section{Potential Pitfalls}
\label{sec:pitfalls}
Combining SRFM and SICM in one setup is bound to bring up some potential
pitfalls, some of which are discussed in the following:

>>>>

\section{Potential Pitfalls}
\label{sec:pitfalls}

\begin{figure}
  \sidecaption
  \includegraphics{gr/pitfalls/CombinedMicroscopy}%
  \caption{\textbf{Potential implementations of combined SICM and FM.} 
  			\textit{Left:} Schematic depiction of potential combined SICM 
  			and TIRF or standard wide-field microscopy (\textit{top}),
  			SICM and z-stacking (\textit{middle}) and SICM and surface
  			scanning (\textit{bottom}). 
  			\textit{Right:} Resulting correlating data of these combinations.}
  \label{fig:CombinedMicroscopy}
\end{figure}

Combining SRFM and SICM in one setup is bound to bring up some potential
pitfalls, some of which are discussed in the following:
